---
title: "Summary_Data_Statistics"
author: "Lucas Wang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

# Import Libraries & Install Packages
library(readxl) # Enables Excel file importing
library(ggplot2) # Enables additonal plot types
library(forcats)
#install.packages("todor") # Enables comment highlighting


```

## Note: prelim analysis focusing on getting presentable values from data

## Importing Excel File

```{r import, include=FALSE}
# sanitized_proposals_withdrawn_removed <- read_excel("sanitized_proposals_withdrawn_removed_and_org_sanitized.xlsx",
#     col_types = c("text", "numeric", "text",
#         "text", "text", "numeric", "numeric",
#         "text", "text", "text", "text", "text",
#         "text", "text", "text", "text", "text",
#         "text", "text", "text", "text", "text",
#         "text"))

sanitized_proposals_withdrawn_removed <- read_excel("sanitized_proposals_withdrawn_removed_and_org_sanitized.xlsx")
```

## Basic Summary

```{r basic_stats}
summary(sanitized_proposals_withdrawn_removed)
```

## Column Analysis

Distribution by year

```{r dist_year}
summary(sanitized_proposals_withdrawn_removed$Year)

ggplot(sanitized_proposals_withdrawn_removed, aes(x=Year)) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), stat = 'count', vjust = -0.5) # NEED to be in this order!!!!!
```

Distribution by Status

```{r dist_status}
summary(sanitized_proposals_withdrawn_removed$Status)

ggplot(sanitized_proposals_withdrawn_removed, aes(x=Status)) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), stat = 'count', vjust = -0.5)
```

Distribution by org: Alphabetical Order

```{r dist_org alph, fig.width=15,fig.height=11}
summary(sanitized_proposals_withdrawn_removed$Organization)

# Alphabetical Orde
ggplot(sanitized_proposals_withdrawn_removed, aes(x=Organization)) +
theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), stat = 'count', vjust = -0.5)
```

Distribution by org: Proposal count high to low order

```{r dist_org high_to_low, fig.width=15,fig.height=11}
# Count of organizational proposal from high to low
ggplot(sanitized_proposals_withdrawn_removed, aes(x=fct_infreq(Organization))) +
theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), stat = 'count', vjust = -0.5)
```
Total requested, total awarded, min_max requested, and min_max awarded

```{r dist_request}
sum(sanitized_proposals_withdrawn_removed$Request)
min(sanitized_proposals_withdrawn_removed$Request)
max(sanitized_proposals_withdrawn_removed$Request)

sum(sanitized_proposals_withdrawn_removed$Award)
min(sanitized_proposals_withdrawn_removed$Award)
max(sanitized_proposals_withdrawn_removed$Award)
```


Distribution by All Requests

```{r dist_request}
summary(sanitized_proposals_withdrawn_removed$Request)

hist(sanitized_proposals_withdrawn_removed$Request)
```

Distribution by All Awards

```{r dist_award}
summary(sanitized_proposals_withdrawn_removed$Award)

hist(sanitized_proposals_withdrawn_removed$Award)
```

Distribution by Request per organization

```{r dist_request}
summary(sanitized_proposals_withdrawn_removed$Request)

hist(sanitized_proposals_withdrawn_removed$Request)
```


Distribution by Award per organization

```{r dist_award}
summary(sanitized_proposals_withdrawn_removed$Award)

hist(sanitized_proposals_withdrawn_removed$Award)
```

Distribution by Abstract Length

```{r dist_org}
summary(sanitized_proposals_withdrawn_removed$Abstract)

```

## Fun Facts:

Longest & shortest abstracts

```{r abs_fun}
min(sanitized_proposals_withdrawn_removed$Request)
max(sanitized_proposals_withdrawn_removed$Award)
```
